---
title: "official updated data with new sample names"
author: "Gabriela R Acevedo Oquendo"
date: '2022-06-30'
output: html_document
---
#Load libraries
```{r}
library("tidyr")
library("dplyr")
library("ggplot2")
library("extrafont")
#font_import()
loadfonts(device = "all")
library("ggpubr")
library("ggsignif")
library("colorspace")
```

## Read data
```{r}
sediment_data <- read.csv("updated_oip copy.csv", stringsAsFactors = TRUE)
#seasons according to the northern hemisphere:
  #spring: March 1 - May 31
  #summer: June 1 - August 31
  #fall: September 1 - November 30
  #winter: December 1 - February 28/29 
  #https://www.timeanddate.com/calendar/aboutseasons.html
```

# Normalized Data column
```{r}

## add to an object so that data frame updates
#change grams to 
  #micrograms = 1000000
  #nanograms = 1000000000
  #microliters = 
#sediment_data %>%
 # select(DNA.Concentration.ng.uL, Elution.uL, Soil.mass.ext_grams) %>%
 # mutate(
    #DNA <- sediment_data$DNA.Concentration.ng.uL,
    #mass <- (sediment_data$Soil.mass.ext_grams * 1000000),
    #elution <- sediment_data$Elution.uL,
  #  NormalizedData <- (sediment_data$DNA.Concentration.ng.uL) * (sediment_data$Elution.uL) * (1/(sediment_data$Soil.mass.ext_grams))
#  )
  
sediment_data_new <- mutate(
  sediment_data, Normalized.Values = sediment_data$DNA.Concentration.ng.uL * sediment_data$Elution.uL * (1/sediment_data$Soil.mass.ext_grams)
)       

print(sediment_data_new)

#normalizeData
```

### plot data - normalized
```{r}

compare_means(Normalized.Values ~ Location, data = sediment_data_new, method = "kruskal.test", p.adjust.methods = "bonferroni" )


dnaconc <- ggplot(data = sediment_data_new, mapping = aes(x = Location, y = Normalized.Values)) + 
  geom_point(mapping = aes(color = Treatment), size = 4, position = position_jitterdodge())+
  geom_boxplot(alpha = 0.4, color = "powderblue", size = 1, outlier.shape =  NA)+
  scale_color_manual(values = c("orchid4", "orchid4"))+ 
  stat_compare_means(method = "kruskal.test", p.adjust.methods="bonferroni" , label.y = 19000) + 
  geom_signif(comparisons = list(c("Duxbury Bay", "Ninigret Pond")), map_signif_level=TRUE, y_position = 12000)+ 
  geom_signif(comparisons = list(c("Ninigret Pond", "RWU")), map_signif_level=TRUE, y_position = 15000)+ 
  geom_signif(comparisons = list(c("RWU", "Saltbox")), map_signif_level=TRUE, y_position = 11000)+
  geom_signif(comparisons = list(c("Town Pond", "Duxbury Bay")), map_signif_level=TRUE, y_position = 17000)+
  geom_signif(comparisons = list(c("Saltbox", "Town Pond")), map_signif_level=TRUE, y_position = 13000)+ 
  
  labs(
    x = "Location",
    y = "DNA Concentration (ng DNA / g sediment)",
    title = "DNA Concentration in Oyster and Bare Sediment Samples Across Locations",
    color = "Treatment"
) + theme(plot.title=element_text(hjust=0.5), legend.position = "none",  panel.background = element_rect(fill = "ivory2"), text = element_text(family = "Times New Roman", size=16))

#t.test(sediment_data_new$Location, sediment_data_new$Normalized.Values)
#dnaconc + stat_compare_means(method = "t.test")
dnaconc



#+ scale_y_continuous(breaks = seq(from=0, to= 40, by= 5), labels = seq(from=0, to=40, by=5))
#axis.text.x = element_text(angle = 90, hjust = 1)
#stat_compare_means(method = "t.test") +



#mapping = aes(color=Treatment, shape = Treatment)
 #scale_color_manual(values = c("lightskyblue2", "plum3"))
#map_signif_level=TRUE)
#geom_signif(comparisons = list(c("Town Pond", "Duxbury Bay")), map_signif_level=TRUE, y_position = 15000)+
#geom_signif(comparisons = list(c("Saltbox", "Town Pond")), map_signif_level=TRUE, y_position = 12000)+ 
#ggsave(filename = "DNAConcentrationNormalizedBonf.png", plot = dnaconc, width = 25, height = 16, dpi = 300, units = "cm")
```




geom_signif(comparisons = list(c("Duxbury Bay", "Ninigret Pond")), map_signif_level=TRUE, y_position = 12000)+ 
  geom_signif(comparisons = list(c("Ninigret Pond", "RWU")), map_signif_level=TRUE, y_position = 15000)+ 
  geom_signif(comparisons = list(c("RWU", "Saltbox")), map_signif_level=TRUE, y_position = 11000)+
  geom_signif(comparisons = list(c("Town Pond", "Duxbury Bay")), map_signif_level=TRUE, y_position = 17000)+
  geom_signif(comparisons = list(c("Saltbox", "Town Pond")), map_signif_level=TRUE, y_position = 13000
  
  
#### plot data - merging all oyster and bare sediment data - normalized
```{r}

#compare_means( Normalized.Values ~ Treatment, data = sediment_data_new, method = "wilcox.test")
compare_means( Normalized.Values ~ Treatment, data = sediment_data_new, method = "t.test")



dnaOB <- ggplot(data = sediment_data_new, mapping = aes(x = Treatment, y = Normalized.Values)) +
  geom_point(mapping = aes(color=Treatment, shape = Treatment), position = position_jitterdodge()) +
  scale_color_manual(values = c("darkseagreen3", "lightsalmon")) + 
  stat_compare_means(method = "t.test", label.y = 25000) + 
  geom_signif(comparisons = list(c("Oyster", "Bare")), map_signif_level=TRUE) +
  geom_boxplot(alpha = 0.3, mapping = aes(color=Treatment), outlier.shape = NA) + 
  labs(
  x = "Sediment Type",
  y = "DNA Concentration (ng DNA / g sediment)",
  title = "DNA Concentration Comparison Between Bare and Oyster Sediments",
  color = "Treatment"
) +
  theme(plot.title=element_text(hjust=0.5), panel.background = element_rect(fill = "ivory2"), text = element_text(family = "Times New Roman", size=12)) 

#kruskal_test <- kruskal.test(Treatment ~ Normalized.Values, data = sediment_data_new)


dnaOB

#+ scale_y_continuous(breaks = seq(from=0, to= 40, by= 5), labels = seq(from=0, to=40, by=5))
#ggsave(filename = "DNAConcOB.Normalized_w_TP.png", plot = dnaOB, width = 20, height = 15, dpi = 300, units = "cm")
```
```{r OvsB-withoutTP}

sediment_data_new_noTP <- 
  sediment_data_new %>%
  dplyr::filter(Location != "Town Pond")

compare_means(Normalized.Values ~ Treatment, data = sediment_data_new_noTP, method = "wilcox.test", paired = TRUE)


dnaOB_no_TP <- ggplot(data = sediment_data_new, mapping = aes(x = Treatment, y = Normalized.Values)) +
  geom_point(mapping = aes(color=Treatment, shape = Treatment), size = 4, position = position_jitterdodge()) +
  scale_color_manual(values = c("darkseagreen3", "lightsalmon")) + 
  stat_compare_means(method = "wilcox.test", label.y = 25000) + 
  geom_signif(comparisons = list(c("Oyster", "Bare")), map_signif_level=TRUE, label.y = 22000) +
  geom_boxplot(alpha = 0.3, mapping = aes(color=Treatment), size = 1, outlier.shape = NA) + 
  labs(
  x = "Sediment Type",
  y = "DNA Concentration (ng DNA / g sediment)",
  title = "DNA Concentration Comparison Between Bare and Oyster Sediments",
  color = "Treatment"
) +
  theme(plot.title=element_text(hjust=0.5), panel.background = element_rect(fill = "ivory2"), text = element_text(family = "Times New Roman", size=12)) 

dnaOB_no_TP

#ggsave(filename = "DNAConcOB.Normalized_no_TP_Bonf.png", plot = dnaOB_no_TP, width = 25, height = 16, dpi = 300, units = "cm")
```





# anova for the second plot
```{r}
#library(ggplot2)
#library(ggpubr)
#library(tidyverse)
#library(broom)
#library(AICcmodavg)

#summary(sediment_data_new)
#OBaov <- read.csv("aovOB.csv", stringsAsFactors = TRUE)
#one.way <- aov(Normalized.Data.1 ~ Normalized.Data.2, data = OBaov)
#summary(one.way)
```
### kruskal wallis for the second plot
```{r}
kruskal.test(Treatment ~ Normalized.Values, data = sediment_data_new)

```

### t-test for second plot
```{r}
t_test <- read.csv("aovOB.csv", stringsAsFactors = TRUE)
t.test(data = t_test, t_test$Normalized.Data.O, t_test$Normalized.Data.B, paired = FALSE)

```

## plotting data without TP - normalized
```{r}
sediment_data_new_noTP <- 
  sediment_data_new %>%
  dplyr::filter(Location != "Town Pond")


gnsd_no_tp <- 
  ggplot(data = sediment_data_new_noTP, mapping = aes(x = Location, y = Normalized.Values,color = Treatment, fill = Treatment)) + 
  
  facet_grid(~Location, scales = "free_x")+
  
  geom_point(mapping = aes(color=Treatment, shape = Treatment), size=2.5, position = position_jitterdodge(jitter.width=0.25)) +
  
  geom_boxplot(alpha = 0.2, outlier.shape = NA) +
  
  scale_color_manual(values = c("darkseagreen3", "lightsalmon"))+ 
  scale_fill_manual(values = c("darkseagreen3", "lightsalmon"))+
  
  stat_compare_means(paired = FALSE, method = "wilcox.test",label.y = 12000, aes(label = paste0("p = ", ..p.format..), )) +
 
  labs(
    x = "Location",
    y = "DNA Concentration (ng DNA / g sediment)",
    title = "DNA Concentration in Oyster and Bare Sediment Samples Across Locations (no TP)",
    color = "Treatment"
) + 
  theme(plot.title=element_text(hjust=0.5), strip.background = element_blank(), strip.text.x = element_blank(), panel.background = element_rect(fill = "ivory2"), text = element_text(family = "Times New Roman", size=16)) 

gnsd_no_tp

#ggsave(filename = "DNAConcNoTPNormBonf.png", plot = nsd_no_tp, width = 22, height = 14, dpi = 300, units = "cm")
#biomass
# geom_signif(comparisons = list(c("Oyster", "Bare")), map_signif_level  =  TRUE) - significance stars
```


""""""

###wilcoxon test for final plot - no TP
```{r}


wilcox_test_df <- read.csv("aovOB.csv", stringsAsFactors = TRUE)


wilcox_testDB <- wilcox.test(data = wilcox_test_df, Location = "Duxbury Bay", wilcox_test_df$Normalized.Data.O, wilcox_test_df$Normalized.Data.B, paired = FALSE)


wilcox_testSB <- wilcox.test(Location = "Saltbox" ~ Normalized.Values, data = wilcox_test_df)
wilcox_testRWU <- wilcox.test(Location = "RWU" ~ Normalized.Values, data = wilcox_test_df)
wilcox_testNP <- wilcox.test(Location = "Ninigret Pond" ~ Normalized.Values, data = wilcox_test_df)  

#dplyr::filter(sediment_data_new, Location != "Town Pond")%>% 
#compare_means(formula, data, method = "wilcox.test", paired = FALSE, group.by = NULL, ref.group = NULL)

#stat_compare_means(mapping = NULL, comparisons = NULL, hide.ns = FALSE, label = NULL,  label.x = NULL, label.y = NULL)

#compare_means(Normalized.Data)
```


